---
title: "bootstrapping"
author: "Kaila Boyer"
date: "11/28/2021"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 7,
  fig.asp = .7,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis",
  scale_colour_discrete = scale_colour_viridis_d,
scale_fill_discrete = scale_fill_viridis_d
)
```

## Simulate a dataset 
```{r}
set.seed(1)
n_samp = 250

sim_df_const = tibble(
  x = rnorm(n_samp, 1, 1), 
  error = rnorm(n_samp, 0, 1), 
  y = 2 + 3 * x + error
)


sim_df_nonconst = sim_df_const %>% 
  mutate(error = error * 0.75 * x, 
         y = 2 + 3 *x + error)
```

make a plot 

```{r}
sim_df_const %>% ggplot(aes(x = x, y = y)) + 
  geom_point()

sim_df_nonconst %>% ggplot(aes(x = x, y = y)) + 
  geom_point()
```

```{r}
sim_df_const %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()

sim_df_nonconst %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```

implement a procedure to get better standard errors in cononst df
## Let's try to use bootstrap for inference 

```{r}
bootstrap_sample <- sim_df_nonconst %>% 
  sample_frac(size = 1, replace = T) %>% 
  arrange(x)
#some observations repeated, some not there at all 

lm(y ~x, data = bootstrap_sample)
```

write a function 
```{r}
boot_sample = function(df) { 
  
  sample_frac(df, size = 1, replace = T)
  }
```

make a tibble to keep track of things 
```{r}
bootstrap_df <- tibble(
  strap_number = 1:1000, 
  strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
)
```

from here, things are kinda the same as "always" 

```{r}
bootstrap_results <- bootstrap_df %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(y ~ x, data = .x)), 
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)

bootstrap_results %>% 
  ggplot(aes(x = estimate)) + 
  geom_histogram() + 
  facet_grid(~term, scales = "free")

lm(y ~ x, data = sim_df_nonconst) %>% broom::tidy()

bootstrap_results %>% 
  group_by(term) %>% 
  summarise(se = sd(estimate))
```
##using models

My goal, of course, isn’t to analyze bootstrap samples by plotting them – I’d like to get a sense of the variability in estimated intercepts and slopes across all my bootstrap samples.

To do that, I’ll use the analytic pipeline we established when looking at nested datasets in linear models: fit the model; tidy the output; unnest and examine the results. The code chunk below uses this pipeline to look at bootstrap standard errors for the estimated regression coefficients.
```{r}
bootstrap_results = 
  bootstrap_df %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) 

bootstrap_results %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)

bootstrap_results %>% 
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))

bootstrap_df %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```

## Bootstrapping function 

```{r}
boostrap_df = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)


#bootstrap_df$strap[[1]]  didnt work 
boostrap_df[[1]][[1]]

as_data_frame(boostrap_df[[1]][[1]])

sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))

sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

## Practice with airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  drop_na(price, stars) %>% 
  select(price, stars, borough, neighborhood, room_type)


nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point()

nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```

